---
title: "MCMC diagnostics"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r, include=FALSE}
library(coda)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(wesanderson)
```

```{r, include=FALSE}
thin <- 500
autoburnin <- FALSE

linewidth.1 = 0.4
linewidth.2 = 0.1

burnin.alpha <- c(
  "yes" = 0.4,
  "no" = 1.0
)

chain.color <- c(
  "1" = wes_palette("AsteroidCity1")[[1]],
  "2" = wes_palette("AsteroidCity1")[[2]]
)

no.legend <- theme(
  legend.position = "none"
)
```

# CRC28

Load chains.

```{r, include=FALSE}
crc28_1 <- read.table(
  "../crc28/results/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)
```

```{r, include=FALSE}
crc28_2 <- read.table(
  "../crc28/results_rep_2/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)
```

## Trace plot

```{r}
crc28.burnin <- 0.1
crc28.len <- min(nrow(crc28_1), nrow(crc28_2))
```

### Loglikelihood

```{r, include=FALSE}
crc28.likelihood <- rbind(
  crc28_1[1:crc28.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 1
    ),
  crc28_2[1:crc28.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 2
    )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r, include=FALSE}
tp.crc28.likelihood.1 <- ggplot(
  crc28.likelihood,
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.likelihood.2 <- ggplot(
  crc28.likelihood %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Ado rate

```{r, include=FALSE}
crc28.ado.rate <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.ado.rate.1 <- ggplot(
  crc28.ado.rate,
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.ado.rate.2 <- ggplot(
  crc28.ado.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Effective sequencing error rate

```{r, include=FALSE}
crc28.eff.seq.err.rate <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.eff.seq.err.rate.1 <- ggplot(
  crc28.eff.seq.err.rate,
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.eff.seq.err.rate.2 <- ggplot(
  crc28.eff.seq.err.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage

```{r, include=FALSE}
crc28.allelic.seq.cov <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.allelic.seq.cov.1 <- ggplot(
  crc28.allelic.seq.cov,
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.allelic.seq.cov.2 <- ggplot(
  crc28.allelic.seq.cov %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage raw variance

```{r, include=FALSE}
crc28.allelic.seq.cov.raw.var <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.allelic.seq.cov.raw.var.1 <- ggplot(
  crc28.allelic.seq.cov.raw.var,
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.allelic.seq.cov.raw.var.2 <- ggplot(
  crc28.allelic.seq.cov.raw.var %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 1

```{r, include=FALSE}
crc28.shape.ctrl.1 <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.shape.ctrl.1.1 <- ggplot(
  crc28.shape.ctrl.1,
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.shape.ctrl.1.2 <- ggplot(
  crc28.shape.ctrl.1 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 2

```{r, include=FALSE}
crc28.shape.ctrl.2 <- rbind(
  crc28_1[1:crc28.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 1
  ),
  crc28_2[1:crc28.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc28.burnin * (crc28.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc28.shape.ctrl.2.1 <- ggplot(
  crc28.shape.ctrl.2,
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc28.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc28.shape.ctrl.2.2 <- ggplot(
  crc28.shape.ctrl.2 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc28.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Plot all

```{r}
tp.crc28 <- ggarrange(
  ggarrange(
    tp.crc28.likelihood.1 + no.legend,
    tp.crc28.ado.rate.1 + no.legend,
    tp.crc28.eff.seq.err.rate.1 + no.legend,
    tp.crc28.allelic.seq.cov.1 + no.legend,
    tp.crc28.allelic.seq.cov.raw.var.1 + no.legend,
    tp.crc28.shape.ctrl.1.1 + no.legend,
    tp.crc28.shape.ctrl.2.1 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "a",
      "c",
      "e",
      "g",
      "i",
      "k",
      "m"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  ggarrange(
    tp.crc28.likelihood.2 + no.legend,
    tp.crc28.ado.rate.2 + no.legend,
    tp.crc28.eff.seq.err.rate.2 + no.legend,
    tp.crc28.allelic.seq.cov.2 + no.legend,
    tp.crc28.allelic.seq.cov.raw.var.2 + no.legend,
    tp.crc28.shape.ctrl.1.2 + no.legend,
    tp.crc28.shape.ctrl.2.2 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "b",
      "d",
      "f",
      "h",
      "j",
      "l",
      "n"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  nrow = 1,
  align = "h",
  common.legend = TRUE,
  legend = "bottom",
  legend.grob = get_legend(tp.crc28.likelihood.1)
)
```

```{r, include=FALSE}
ggsave(
  "../figs/crc28_trace_plot.pdf",
  tp.crc28,
  device = "pdf",
  width = 183,
  height = 252,
  units = "mm",
  dpi = 300
)
```

## Gelman-Rubin's criterion

### Ado rate

```{r}
gr.crc28.ado.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.ado.rate,
          chain == 1,
          burnin == "no"
        )$adoRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.ado.rate,
          chain == 2,
          burnin == "no"
        )$adoRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.ado.rate
```

### Effective sequencing error rate

```{r}
gr.crc28.eff.seq.err.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.eff.seq.err.rate,
          chain == 1,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.eff.seq.err.rate,
          chain == 2,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.eff.seq.err.rate
```

### Allelic sequencing coverage

```{r}
gr.crc28.allelic.seq.cov <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.allelic.seq.cov,
          chain == 1,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.allelic.seq.cov,
          chain == 2,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.allelic.seq.cov
```

### Allelic sequencing coverage raw variance

```{r}
gr.crc28.allelic.seq.cov.raw.var <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.allelic.seq.cov.raw.var,
          chain == 1,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.allelic.seq.cov.raw.var,
          chain == 2,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.allelic.seq.cov.raw.var
```

### Shape controller 1

```{r}
gr.crc28.shape.ctrl.1 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.shape.ctrl.1,
          chain == 1,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.shape.ctrl.1,
          chain == 2,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.shape.ctrl.1
```

### Shape controller 2

```{r}
gr.crc28.shape.ctrl.2 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc28.shape.ctrl.2,
          chain == 1,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc28.shape.ctrl.2,
          chain == 2,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc28.shape.ctrl.2
```

# CRC48

## Load chains

```{r}
crc48_1 <- read.table(
  "../crc48/results/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)[1:8001, ]
```

```{r}
crc48_2 <- read.table(
  "../crc48/results_rep_2/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)
```

## Trace plot

```{r}
crc48.burnin <- 0.1
crc48.len <- min(nrow(crc48_1), nrow(crc48_2))
```

### Loglikelihood

```{r, include=FALSE}
crc48.likelihood <- rbind(
  crc48_1[1:crc48.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 1
    ),
  crc48_2[1:crc48.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 2
    )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r, include=FALSE}
tp.crc48.likelihood.1 <- ggplot(
  crc48.likelihood,
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.likelihood.2 <- ggplot(
  crc48.likelihood %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Ado rate

```{r, include=FALSE}
crc48.ado.rate <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.ado.rate.1 <- ggplot(
  crc48.ado.rate,
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.ado.rate.2 <- ggplot(
  crc48.ado.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Effective sequencing error rate

```{r, include=FALSE}
crc48.eff.seq.err.rate <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.eff.seq.err.rate.1 <- ggplot(
  crc48.eff.seq.err.rate,
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.eff.seq.err.rate.2 <- ggplot(
  crc48.eff.seq.err.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage

```{r, include=FALSE}
crc48.allelic.seq.cov <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.allelic.seq.cov.1 <- ggplot(
  crc48.allelic.seq.cov,
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.allelic.seq.cov.2 <- ggplot(
  crc48.allelic.seq.cov %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage raw variance

```{r, include=FALSE}
crc48.allelic.seq.cov.raw.var <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.allelic.seq.cov.raw.var.1 <- ggplot(
  crc48.allelic.seq.cov.raw.var,
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.allelic.seq.cov.raw.var.2 <- ggplot(
  crc48.allelic.seq.cov.raw.var %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 1

```{r, include=FALSE}
crc48.shape.ctrl.1 <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.shape.ctrl.1.1 <- ggplot(
  crc48.shape.ctrl.1,
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.shape.ctrl.1.2 <- ggplot(
  crc48.shape.ctrl.1 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 2

```{r, include=FALSE}
crc48.shape.ctrl.2 <- rbind(
  crc48_1[1:crc48.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 1
  ),
  crc48_2[1:crc48.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= crc48.burnin * (crc48.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.crc48.shape.ctrl.2.1 <- ggplot(
  crc48.shape.ctrl.2,
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(crc48.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.crc48.shape.ctrl.2.2 <- ggplot(
  crc48.shape.ctrl.2 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(crc48.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Plot all

```{r}
tp.crc48 <- ggarrange(
  ggarrange(
    tp.crc48.likelihood.1 + no.legend,
    tp.crc48.ado.rate.1 + no.legend,
    tp.crc48.eff.seq.err.rate.1 + no.legend,
    tp.crc48.allelic.seq.cov.1 + no.legend,
    tp.crc48.allelic.seq.cov.raw.var.1 + no.legend,
    tp.crc48.shape.ctrl.1.1 + no.legend,
    tp.crc48.shape.ctrl.2.1 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "a",
      "c",
      "e",
      "g",
      "i",
      "k",
      "m"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  ggarrange(
    tp.crc48.likelihood.2 + no.legend,
    tp.crc48.ado.rate.2 + no.legend,
    tp.crc48.eff.seq.err.rate.2 + no.legend,
    tp.crc48.allelic.seq.cov.2 + no.legend,
    tp.crc48.allelic.seq.cov.raw.var.2 + no.legend,
    tp.crc48.shape.ctrl.1.2 + no.legend,
    tp.crc48.shape.ctrl.2.2 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "b",
      "d",
      "f",
      "h",
      "j",
      "l",
      "n"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  nrow = 1,
  align = "h",
  common.legend = TRUE,
  legend = "bottom",
  legend.grob = get_legend(tp.crc48.likelihood.1)
)
```

```{r, include=FALSE}
ggsave(
  "../figs/crc48_trace_plot.pdf",
  tp.crc48,
  device = "pdf",
  width = 183,
  height = 252,
  units = "mm",
  dpi = 300
)
```

## Gelman-Rubin's criterion

### Ado rate

```{r}
gr.crc48.ado.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.ado.rate,
          chain == 1,
          burnin == "no"
        )$adoRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.ado.rate,
          chain == 2,
          burnin == "no"
        )$adoRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.ado.rate
```

### Effective sequencing error rate

```{r}
gr.crc48.eff.seq.err.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.eff.seq.err.rate,
          chain == 1,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.eff.seq.err.rate,
          chain == 2,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.eff.seq.err.rate
```

### Allelic sequencing coverage

```{r}
gr.crc48.allelic.seq.cov <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.allelic.seq.cov,
          chain == 1,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.allelic.seq.cov,
          chain == 2,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.allelic.seq.cov
```

### Allelic sequencing coverage raw variance

```{r}
gr.crc48.allelic.seq.cov.raw.var <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.allelic.seq.cov.raw.var,
          chain == 1,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.allelic.seq.cov.raw.var,
          chain == 2,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.allelic.seq.cov.raw.var
```

### Shape controller 1

```{r}
gr.crc48.shape.ctrl.1 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.shape.ctrl.1,
          chain == 1,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.shape.ctrl.1,
          chain == 2,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.shape.ctrl.1
```

### Shape controller 2

```{r}
gr.crc48.shape.ctrl.2 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          crc48.shape.ctrl.2,
          chain == 1,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          crc48.shape.ctrl.2,
          chain == 2,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.crc48.shape.ctrl.2
```

# TNBC16

## Load chains

```{r}
tnbc16_1 <- read.table(
  "../tnbc16/results/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)
```

```{r}
tnbc16_2 <- read.table(
  "../tnbc16/results_rep_2/stage1/phylogenetic_inference_dir/rmc_mudel_sa_stage_1/rmc_mudel_sa_stage_1.log",
  header = TRUE
)
```

## Trace plot

```{r}
tnbc16.burnin <- 0.1
tnbc16.len <- min(nrow(tnbc16_1), nrow(tnbc16_2))
```

### Loglikelihood

```{r, include=FALSE}
tnbc16.likelihood <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 1
    ),
  tnbc16_2[1:tnbc16.len, ] %>%
    mutate(
      likelihood = likelihood1 + likelihood2
    ) %>%
    select(
      Sample,
      likelihood
    ) %>%
    mutate(
      chain = 2
    )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r, include=FALSE}
tp.tnbc16.likelihood.1 <- ggplot(
  tnbc16.likelihood,
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.likelihood.2 <- ggplot(
  tnbc16.likelihood %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = likelihood,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.likelihood, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Loglikelihood") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Ado rate

```{r, include=FALSE}
tnbc16.ado.rate <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    adoRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.ado.rate.1 <- ggplot(
  tnbc16.ado.rate,
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.ado.rate.2 <- ggplot(
  tnbc16.ado.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = adoRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.ado.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("ADO rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Effective sequencing error rate

```{r, include=FALSE}
tnbc16.eff.seq.err.rate <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    effSeqErrRate
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.eff.seq.err.rate.1 <- ggplot(
  tnbc16.eff.seq.err.rate,
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.eff.seq.err.rate.2 <- ggplot(
  tnbc16.eff.seq.err.rate %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = effSeqErrRate,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.eff.seq.err.rate, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Effective sequencing\nerror rate") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage

```{r, include=FALSE}
tnbc16.allelic.seq.cov <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    allelicSeqCov
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.allelic.seq.cov.1 <- ggplot(
  tnbc16.allelic.seq.cov,
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.allelic.seq.cov.2 <- ggplot(
  tnbc16.allelic.seq.cov %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCov,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.allelic.seq.cov, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Allelic sequencing coverage raw variance

```{r, include=FALSE}
tnbc16.allelic.seq.cov.raw.var <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    allelicSeqCovRawVar
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.allelic.seq.cov.raw.var.1 <- ggplot(
  tnbc16.allelic.seq.cov.raw.var,
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.allelic.seq.cov.raw.var.2 <- ggplot(
  tnbc16.allelic.seq.cov.raw.var %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = allelicSeqCovRawVar,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.allelic.seq.cov.raw.var, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Allelic sequencing\ncoverage raw variance") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 1

```{r, include=FALSE}
tnbc16.shape.ctrl.1 <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    shapeCtrl1
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.shape.ctrl.1.1 <- ggplot(
  tnbc16.shape.ctrl.1,
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.shape.ctrl.1.2 <- ggplot(
  tnbc16.shape.ctrl.1 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl1,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.shape.ctrl.1, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 1") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Shape controller 2

```{r, include=FALSE}
tnbc16.shape.ctrl.2 <- rbind(
  tnbc16_1[1:tnbc16.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 1
  ),
  tnbc16_2[1:tnbc16.len, ] %>%
  select(
    Sample,
    shapeCtrl2
  ) %>%
  mutate(
    chain = 2
  )
) %>%
  mutate(
    chain = factor(chain, levels = c(1, 2))
  ) %>%
  mutate(
    burnin = if_else(
      Sample <= tnbc16.burnin * (tnbc16.len - 1) * thin,
      "yes",
      "no"
    )
  )
```

```{r}
tp.tnbc16.shape.ctrl.2.1 <- ggplot(
  tnbc16.shape.ctrl.2,
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.1
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    legend.position = "bottom",
    panel.grid = element_blank()
  )

tp.tnbc16.shape.ctrl.2.2 <- ggplot(
  tnbc16.shape.ctrl.2 %>%
    filter(
      burnin == "no"
    ),
  aes(
    x = Sample,
    y = shapeCtrl2,
    shape = chain,
    color = chain,
    alpha = burnin
  )
) +
  geom_line(
    linewidth = linewidth.2
  ) +
  geom_vline(
    xintercept = max(filter(tnbc16.shape.ctrl.2, burnin == "yes")$Sample),
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  ylab("Shape controller 2") +
  scale_color_manual(
    values = chain.color
  ) +
  scale_alpha_manual(
    values = burnin.alpha
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid = element_blank()
  )
```

### Plot all

```{r}
tp.tnbc16 <- ggarrange(
  ggarrange(
    tp.tnbc16.likelihood.1 + no.legend,
    tp.tnbc16.ado.rate.1 + no.legend,
    tp.tnbc16.eff.seq.err.rate.1 + no.legend,
    tp.tnbc16.allelic.seq.cov.1 + no.legend,
    tp.tnbc16.allelic.seq.cov.raw.var.1 + no.legend,
    tp.tnbc16.shape.ctrl.1.1 + no.legend,
    tp.tnbc16.shape.ctrl.2.1 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "a",
      "c",
      "e",
      "g",
      "i",
      "k",
      "m"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  ggarrange(
    tp.tnbc16.likelihood.2 + no.legend,
    tp.tnbc16.ado.rate.2 + no.legend,
    tp.tnbc16.eff.seq.err.rate.2 + no.legend,
    tp.tnbc16.allelic.seq.cov.2 + no.legend,
    tp.tnbc16.allelic.seq.cov.raw.var.2 + no.legend,
    tp.tnbc16.shape.ctrl.1.2 + no.legend,
    tp.tnbc16.shape.ctrl.2.2 + no.legend,
    ncol = 1,
    align = "v",
    heights = c(
      rep(
        1,
        6
      ),
      1.2
    ),
    labels = c(
      "b",
      "d",
      "f",
      "h",
      "j",
      "l",
      "n"
    ),
    font.label = list(face = "bold", size = 7)
  ),
  nrow = 1,
  align = "h",
  common.legend = TRUE,
  legend = "bottom",
  legend.grob = get_legend(tp.tnbc16.likelihood.1)
)
```

```{r, include=FALSE}
ggsave(
  "../figs/tnbc16_trace_plot.pdf",
  tp.tnbc16,
  device = "pdf",
  width = 183,
  height = 252,
  units = "mm",
  dpi = 300
)
```

## Gelman-Rubin's criterion

### Ado rate

```{r}
gr.tnbc16.ado.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.ado.rate,
          chain == 1,
          burnin == "no"
        )$adoRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.ado.rate,
          chain == 2,
          burnin == "no"
        )$adoRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.ado.rate
```

### Effective sequencing error rate

```{r}
gr.tnbc16.eff.seq.err.rate <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.eff.seq.err.rate,
          chain == 1,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.eff.seq.err.rate,
          chain == 2,
          burnin == "no"
        )$effSeqErrRate,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.eff.seq.err.rate
```

### Allelic sequencing coverage

```{r}
gr.tnbc16.allelic.seq.cov <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.allelic.seq.cov,
          chain == 1,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.allelic.seq.cov,
          chain == 2,
          burnin == "no"
        )$allelicSeqCov,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.allelic.seq.cov
```

### Allelic sequencing coverage raw variance

```{r}
gr.tnbc16.allelic.seq.cov.raw.var <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.allelic.seq.cov.raw.var,
          chain == 1,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.allelic.seq.cov.raw.var,
          chain == 2,
          burnin == "no"
        )$allelicSeqCovRawVar,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.allelic.seq.cov.raw.var
```

### Shape controller 1

```{r}
gr.tnbc16.shape.ctrl.1 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.shape.ctrl.1,
          chain == 1,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.shape.ctrl.1,
          chain == 2,
          burnin == "no"
        )$shapeCtrl1,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.shape.ctrl.1
```

### Shape controller 2

```{r}
gr.tnbc16.shape.ctrl.2 <- gelman.diag(
  mcmc.list(
    list(
      c1 = mcmc(
        filter(
          tnbc16.shape.ctrl.2,
          chain == 1,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      ),
      c2 = mcmc(
        filter(
          tnbc16.shape.ctrl.2,
          chain == 2,
          burnin == "no"
        )$shapeCtrl2,
        thin = 500
      )
    )
  ),
  autoburnin = autoburnin
)

gr.tnbc16.shape.ctrl.2
```

# Plot Gelman-Rubin's potential scale reduction factor

```{r}
data.frame(
  reduction_factor = vapply(
    list(
      gr.crc28.ado.rate,
      gr.crc28.eff.seq.err.rate,
      gr.crc28.allelic.seq.cov,
      gr.crc28.allelic.seq.cov.raw.var,
      gr.crc28.shape.ctrl.1,
      gr.crc28.shape.ctrl.2,
      gr.crc48.ado.rate,
      gr.crc48.eff.seq.err.rate,
      gr.crc48.allelic.seq.cov,
      gr.crc48.allelic.seq.cov.raw.var,
      gr.crc48.shape.ctrl.1,
      gr.crc48.shape.ctrl.2,
      gr.tnbc16.ado.rate,
      gr.tnbc16.eff.seq.err.rate,
      gr.tnbc16.allelic.seq.cov,
      gr.tnbc16.allelic.seq.cov.raw.var,
      gr.tnbc16.shape.ctrl.1,
      gr.tnbc16.shape.ctrl.2
    ),
    function(x) x$psrf[1, 1],
    FUN.VALUE = numeric(1),
    USE.NAMES = FALSE
  ),
  dataset = rep(
    c("CRC28", "CRC48", "TNBC16"),
    each = 6
  )
) %>%
  mutate(
    dataset = factor(
      dataset,
      levels = c("TNBC16", "CRC28", "CRC48")
    )
  ) %>%
  ggplot(
    aes(
      x = dataset, y = reduction_factor
    )
  ) +
  geom_violin() +
  geom_point(
    position = position_jitterdodge(
      seed = 1
    ),
    aes(alpha = dataset),
    color = "gray43",
    size = 3 / .pt
  ) +
  geom_hline(
    yintercept = 1.1,
    linetype="dashed",
    color = "gray43",
    size = 1 / .pt
  ) +
  scale_alpha_discrete(
    breaks = c("TNBC16", "CRC28", "CRC48"),
    range = c(0.7, 0.7)
  ) +
  labs(
    x = "Dataset",
    y = "Gelman-Rubin statistic"
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 7),
    legend.position = "none",
    panel.grid = element_blank()
  )

ggsave(
  "../figs/gelman_rubin_statistic.pdf",
  device = "pdf",
  width = 120,
  height = 70,
  units = "mm",
  dpi = 300
)
```
