---
title: "R Notebook"
author: senbaikang
date: 20.03.21
output:
  pdf_document: default
  html_notebook: default
---

## Constants

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# "ld" for locus dropout; "sa" for single ado
ADO_MODE <- "sa"

# "delsieve" or "sieve
CONFIG = "delsieve"

INPUT_DATA_FILE <- paste("../tnbc16", "data", "W32_dataFilter_improved.tsv", sep = "/")
MUT_ROWS <- 5912

REF_CLONE_WISE_CNVS_FILES <- list(
  "Cancer" = paste(
    "../tnbc16",
    "data",
    "W32_segments.txt",
    sep = "/"
  )
)
REF_CLONE_WISE_INDELS_FILE <- paste("../tnbc16", "data", "W32_mutect_indels.vcf", sep = "/")

DELSIEVE_PREFIX <- paste("../tnbc16", ADO_MODE, CONFIG, sep = "/")

CELL_ORIGIN <- NULL
PLOT_BRANCH_LENGTH <- TRUE
PLOT_HPD <- TRUE
SCALE_LONGEST_BRANCH <- 1 # 2

DELSIEVE_RESULTS_DIR <- paste0(
  DELSIEVE_PREFIX,
  "/../../results/stage2/variant_calling_dir/rmc_mu",
  ifelse(
    CONFIG == "delsieve",
    "del_",
    "_"
  ),
  ADO_MODE,
  "_stage_1-rmc_mu",
  ifelse(
    CONFIG == "delsieve",
    "del_",
    "_"
  ),
  ADO_MODE,
  "_stage_2/"
)

DELSIEVE_VCF_FILE <- paste0(
  DELSIEVE_RESULTS_DIR,
  "rmc_mu",
  ifelse(
    CONFIG == "delsieve",
    "del_",
    "_"
  ),
  ADO_MODE,
  "_stage_1-rmc_mu",
  ifelse(
    CONFIG == "delsieve",
    "del_",
    "_"
  ),
  ADO_MODE,
  "_stage_2_mode_gaussian.vcf"
)
DELSIEVE_VCF <- paste(DELSIEVE_PREFIX, "geneannotator/delsieve_vcf.rds", sep = "/")

SIEVE_VCF <- paste("../tnbc16", "data", "sieve_vcf.rds", sep = "/")
```

## Load helper functions

```{r warning = FALSE}
source(file = "real_data_visualization.R")
```

## Visualize tree

### Load local tree and get tips

```{r}
tree <- read.beast(paste(DELSIEVE_PREFIX, "geneannotator/annotated.tree", sep = "/"))

tip.df <- get.tip.info(tree, pat2names = CELL_ORIGIN)

ordered.tips <- get.ordered.tip.names(tree)
```

### Plot tree with nodes

```{r}
tree.branch.size <- 2.0 / .pt
tree.out.format <- cairo_pdf
tree.out.dpi <- 300
tree.out.limitsize <- FALSE
tip.point.size <- 4 / .pt
tip.label.align <- TRUE
tip.label.linetype <- "dotted"
tip.label.linesize <- 1 / .pt
tip.label.size <- 7 / .pt
tip.label.color <- get.tip.color(1)
tip.label.legend.title <- "Cell origin"
legend.spacing <- unit(0, "pt")
legend.key.size <- unit(3, "mm")
legend.text.size <- element_text(size = 7)
legend.title.size <- element_text(size = 7)

mark.complex.genes <- list(
  general = TRUE,
  strict = TRUE
)
gene.dup.gene.sep <- " \U00D7 "
gene.sep.criterion <- tibble(
    num = c(3, 10, 15, 20, 30, 40, 50, 100, 150, 200, 250, 300),#c(10, 20, 40, 60, 80, 100, 120, 150, 200, 250, 300),#
    group = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
  )
gene.sep.collapse <- ","
gene.text.alpha <- 0.9
gene.text.size <- 6 / .pt
gene.text.repel.min.segment.length <- 0
gene.text.repel.max.overlaps <- 100
gene.text.repel.label.padding <- unit(0.1, "lines")
gene.text.repel.point.padding <- unit(0, "lines")
gene.label.repel.label.r <- unit(0.1, "lines")
gene.label.repel.label.size <- unit(0.15, "mm")
gene.legend.title <- "Mutation event"
gene.repel.type <- "label" # "label" or "text"
gene.text.color.type <- "color" # "fill" or "color" / "colour"
```

Plot a tree with HPD.

```{r}
if (PLOT_HPD) {
  plot.nodes(
    tree.plot = get.ggtree(
      tree,
      branch.alpha = 1.0,
      plot.branch.length = TRUE,
      branch.size = tree.branch.size,
      scale.longest.branch = 1L
    ),
    anno.tip.text = FALSE,
    anno.tip.label = TRUE,
    tip.data = tip.df,
    tip.point.size = tip.point.size,
    tip.label.align = tip.label.align,
    tip.label.linetype = tip.label.linetype,
    tip.label.linesize = tip.label.linesize,
    tip.label.offset = 0,
    tip.label.size = tip.label.size,
    tip.label.legend.title = tip.label.legend.title,
    tip.label.color = tip.label.color,
    x.limit = c(0, 0.00017),
    legend.spacing = legend.spacing,
    legend.pos = c(0, 1),
    legend.just = c("left", "top"),
    legend.direction = "vertical",
    legend.key.size = legend.key.size,
    legend.text.size = legend.text.size,
    legend.title.size = legend.title.size,
    plot.margin = unit(c(0, 0, 0, 0), "mm"),
    anno.hpd = TRUE,
    hpd.color = "red",
    hpd.size = 3 / .pt,
    hpd.alpha = 1.0,
    anno.branch.length = FALSE,
    branch.length.digit = 3L,
    branch.length.text.size = 7L / .pt,
    branch.length.color = "lightblue",
    branch.length.alpha = 1.0,
    label.repel.arrow.length = unit(1.2, "mm"),
    label.repel.force = 1,
    label.repel.force_pull = 1,
    label.repel.min.segment.length = 0,
    label.repel.max.overlaps = 100,
    label.repel.label.padding = unit(0.1, "lines"),
    label.repel.box.padding = unit(0.1, "lines"),
    label.repel.label.r = unit(0.1, "lines"),
    label.repel.label.size = unit(0.15, "mm"),
    anno.support = FALSE,
    seed = 1L,
    out.file = paste(DELSIEVE_PREFIX, "geneannotator/tree_HPD.pdf", sep = "/"),
    out.format = tree.out.format,
    out.width = 183,
    out.height = 80,
    out.dpi = tree.out.dpi,
    out.limitsize = tree.out.limitsize
  )
}
```

Plot a tree with genes annotated.

```{r}
tree.plot <- get.ggtree(
  tree,
  plot.branch.length = PLOT_BRANCH_LENGTH,
  branch.size = tree.branch.size,
  scale.longest.branch = SCALE_LONGEST_BRANCH
)
tree.plot <- plot.nodes(
  tree.plot = tree.plot,
  tip.data = tip.df,
  tip.point.size = tip.point.size,
  tip.label.align = tip.label.align,
  tip.label.linetype = tip.label.linetype,
  tip.label.linesize = tip.label.linesize,
  tip.label.offset = 0.000003, # 0.0000015
  tip.label.size = tip.label.size,
  tip.label.legend.title = tip.label.legend.title,
  tip.label.color = tip.label.color,
  x.limit = c(0, 0.00017), # 0.0000585
  legend.spacing = legend.spacing,
  legend.pos = c(0, 0.715), #c(0.68, 0.082)
  legend.just = c("left", "top"),
  legend.direction = "vertical",
  legend.key.size = legend.key.size,
  legend.text.size = legend.text.size,
  legend.title.size = legend.title.size,
  plot.margin = unit(c(0, 0, 0, 0), "mm"),
  support.threshold = 0.5,
  internal.node.text.size = 7 / .pt,
  internal.node.label.padding = unit(0.1, "lines"),
  internal.node.label.r = unit(0.1, "lines"),
  internal.node.label.size = unit(0.15, "mm"),
  internal.node.label.alpha = 1.0,
  internal.node.label.fill.color = "white"
)
tree.plot
```

1.  All genes.

```{r}
tree.plot.1 <- plot.genes(
  tree.plot,
  mode = 1L,
  mark.complex.genes = mark.complex.genes,
  dup.gene.sep = gene.dup.gene.sep,
  criterion = gene.sep.criterion,
  collapse = gene.sep.collapse,
  text.alpha = gene.text.alpha,
  text.size = gene.text.size,
  # arrow.length = unit(1, "mm"),
  # arrow.type = "open",
  text.repel.force = 20,
  text.repel.force_pull = 1,
  text.repel.min.segment.length = gene.text.repel.min.segment.length,
  text.repel.max.overlaps = 30,
  text.repel.label.padding = gene.text.repel.label.padding,
  text.repel.box.padding = unit(1, "lines"),
  text.repel.point.padding = gene.text.repel.point.padding,
  label.repel.label.r = gene.label.repel.label.r,
  label.repel.label.size = gene.label.repel.label.size,
  legend.title = gene.legend.title,
  repel.type = gene.repel.type, # "label" or "text"
  text.color.type = gene.text.color.type, # "fill" or "color" / "colour"
  direction = "both",
  seed = 10L,
  out.file = paste0(DELSIEVE_PREFIX, "/geneannotator/tree_all.pdf"),
  out.format = tree.out.format,
  out.width = 183,
  out.height = 252,
  out.dpi = tree.out.dpi,
  out.limitsize = tree.out.limitsize
)
tree.plot.1
```

2.  ISA genes.

```{r}
# tree.plot.2 <- plot.genes(
#   tree.plot,
#   mode = 2L,
#   dup.gene.sep = gene.dup.gene.sep,
#   criterion = gene.sep.criterion,
#   collapse = gene.sep.collapse,
#   text.alpha = gene.text.alpha,
#   text.size = gene.text.size,
#   # arrow.length = unit(1, "mm"),
#   # arrow.type = "open",
#   text.repel.force = 1,
#   text.repel.force_pull = 1,
#   text.repel.min.segment.length = gene.text.repel.min.segment.length,
#   text.repel.max.overlaps = 100,
#   text.repel.label.padding = gene.text.repel.label.padding,
#   text.repel.box.padding = unit(1.5, "lines"),
#   text.repel.point.padding = gene.text.repel.point.padding,
#   label.repel.label.r = gene.label.repel.label.r,
#   label.repel.label.size = gene.label.repel.label.size,
#   legend.title = gene.legend.title,
#   repel.type = gene.repel.type, # "label" or "text"
#   text.color.type = gene.text.color.type, # "fill" or "color" / "colour"
#   seed = 2000L,
#   out.file = paste0(SIEVE_PREFIX, "/geneannotator/tree_isa.pdf"),
#   out.format = tree.out.format,
#   out.width = 183,
#   out.height = 247,
#   out.dpi = tree.out.dpi,
#   out.limitsize = tree.out.limitsize
# )
# tree.plot.2
```

3.  FSA genes.

```{r}
# tree.plot.3 <- plot.genes(
#   tree.plot,
#   mode = 3L,
#   dup.gene.sep = gene.dup.gene.sep,
#   criterion = gene.sep.criterion,
#   collapse = gene.sep.collapse,
#   text.alpha = gene.text.alpha,
#   text.size = gene.text.size,
#   # arrow.length = unit(1, "mm"),
#   # arrow.type = "open",
#   text.repel.force = 1,
#   text.repel.force_pull = 1,
#   text.repel.min.segment.length = gene.text.repel.min.segment.length,
#   text.repel.max.overlaps = 50,
#   text.repel.label.padding = gene.text.repel.label.padding,
#   text.repel.box.padding = unit(0.3, "lines"),
#   text.repel.point.padding = gene.text.repel.point.padding,
#   label.repel.label.r = gene.label.repel.label.r,
#   label.repel.label.size = gene.label.repel.label.size,
#   legend.title = gene.legend.title,
#   repel.type = gene.repel.type, # "label" or "text"
#   text.color.type = gene.text.color.type, # "fill" or "color" / "colour"
#   seed = 10L,
#   out.file = paste0(SIEVE_PREFIX, "/geneannotator/tree_fsa.pdf"),
#   out.format = tree.out.format,
#   out.width = 180,
#   out.height = 130,
#   out.dpi = tree.out.dpi,
#   out.limitsize = tree.out.limitsize
# )
# tree.plot.3
```

## Visualize genotype heatmap

### Load data from VCF files

```{r}
if (is.null(DELSIEVE_VCF) || !file.exists(DELSIEVE_VCF)) {
  delsieveVCF <- loadVcf(
    file = DELSIEVE_VCF_FILE,
    local.copy = DELSIEVE_VCF,
    cores = 4L
  )
} else {
  delsieveVCF <- readRDS(DELSIEVE_VCF)
}

size.factors <- load.size.factors(DELSIEVE_RESULTS_DIR)

ref.indelVCF <- loadVcf(
  file = REF_CLONE_WISE_INDELS_FILE,
  vcf.geno = c("GT"),
  convert2ternary = FALSE,
  cores = 1L
)

ref.cn.comp <- get.cn.comp(
  REF_CLONE_WISE_CNVS_FILES,
  delsieveVCF
)

cov.data <- load.cov.data(
  INPUT_DATA_FILE,
  MUT_ROWS,
  colnames(delsieveVCF),
  size.factors = size.factors
)
```

### Color mapping function

```{r}
ht_opt(
  "COLUMN_ANNO_PADDING" = unit(0.5, "mm"),
  "fast_hclust" = TRUE,
  "verbose" = TRUE
)

out.gt.hm.width <- 183 # mm
out.gt.hm.height <- 50 # mm
in2mm <- 25.4

gpar.title <- gpar(fontsize = 8L, fontfamily = "sans")
gpar.title.2 <- gpar(fontsize = 8L, fontfamily = "sans")
gpar.text <- gpar(fontsize = 7L, fontfamily = "sans")

color.gt.hm <- get.gt.hm.color(i = 2)
hm.row.title <- "Cells"
hm.row.title.side <- "left"
hm.row.title.gp <- gpar.title.2
hm.column.title <- "SNV sites"
hm.column.title.side <- "top"
hm.column.title.gp <- gpar.title.2
hm.row.order <- ordered.tips
hm.row.names.side <- "left"
hm.row.names.gp <- gpar.text
hm.col.names.side <- "bottom"
hm.col.names.gp <- gpar.text
hm.col.names.rot <- 45
```

### Prepare data for heatmap

```{r}
delsieve.gt.data <- get.ternary(delsieveVCF)
delsieve.gt.legend <- get.gt.legend(delsieve.gt.data, is.ado = FALSE)

cov.data <- cov.data[decompose.sites(rownames(delsieve.gt.data))$site, ]
```

### Genotype heatmap from Sieve

Cells are ordered according to the above tree, and sites are ordered with a specified distance method.

```{r}
delsieve.gt.hm <- Heatmap(
  t(delsieve.gt.data),
  col = color.gt.hm,
  row_title = hm.row.title,
  row_title_side = hm.row.title.side,
  row_title_gp = hm.row.title.gp,
  column_title = hm.column.title,
  column_title_side = hm.column.title.side,
  column_title_gp = hm.column.title.gp,
  cluster_rows = FALSE,
  row_order = hm.row.order,
  row_names_side = hm.row.names.side,
  row_names_gp = hm.row.names.gp,
  row_names_centered = TRUE,
  show_column_dend = FALSE,
  show_row_names = FALSE,
  show_column_names = FALSE,
  heatmap_legend_param = list(
    at = as.integer(names(delsieve.gt.legend)),
    labels = delsieve.gt.legend,
    title = "Genotype",
    grid_height = unit(3, "mm"),
    grid_width = unit(3, "mm"),
    color_bar = "discrete",
    border = "black",
    title_gp = gpar.title,
    labels_gp = gpar.text
  )
)

draw(delsieve.gt.hm)

delsieve.gt.hm.column.order <- column_order(delsieve.gt.hm)

gt.key.sites <- columnAnnotation(
    labelled_sites = anno_mark(
      at = c(
        delsieve.gt.hm.column.order[1L],
        delsieve.gt.hm.column.order[2000L],
        delsieve.gt.hm.column.order[4000L],
        delsieve.gt.hm.column.order[length(delsieve.gt.hm.column.order)]
        ),
      labels = get.formatted.num.as.char(c(
        "1",
        "2000",
        "4000",
        as.character(length(delsieve.gt.hm.column.order))
        )),
      which = "column",
      side = "top",
      labels_gp = gpar.text,
      labels_rot = 0,
      link_width = unit(1, "pt"),
      link_height = unit(2, "pt")
    ),
    show_legend = FALSE
  )

delsieve.gt.hm.column.order <- rownames(delsieveVCF)[delsieve.gt.hm.column.order]

ordered.cn.for.gt <- tibble(site = delsieve.gt.hm.column.order) %>%
  separate_wider_delim(site, delim = "_", names = c("site", "tmp")) %>%
  select(-tmp) %>%
  left_join(
    ref.cn.comp,
    by = "site",
    multiple = "all"
  )

# cn.info.for.gt <- columnAnnotation(
#   "Cancer" = anno_lines(
#     filter(ordered.cn.for.gt, clone == "Cancer")$CNt,
#     gp = gpar(col = "gray43"),
#     size = unit(0.05, "pt"),
#     height = unit(out.gt.hm.height / 8, "mm"),
#     border = FALSE,
#     axis_param = list(
#       at = c(0, 2),
#       gp = gpar.small
#     )
#   ),
#   annotation_name_gp = gpar.small,
#   show_legend = FALSE
# )

cairo_pdf(
  paste(DELSIEVE_PREFIX, "geneannotator/gt_delsieve.pdf", sep = "/"),
  width = out.gt.hm.width / in2mm,
  height = out.gt.hm.height / in2mm,
  fallback_resolution = 300,
  onefile = FALSE
)

delsieve.gt.hm <- Heatmap(
  t(delsieve.gt.data),
  col = color.gt.hm,
  row_title = hm.row.title,
  row_title_side = hm.row.title.side,
  row_title_gp = hm.row.title.gp,
  column_title = hm.column.title,
  column_title_side = hm.column.title.side,
  column_title_gp = hm.column.title.gp,
  cluster_rows = FALSE,
  row_order = hm.row.order,
  column_order = delsieve.gt.hm.column.order,
  row_names_side = hm.row.names.side,
  row_names_gp = hm.row.names.gp,
  row_names_centered = TRUE,
  show_column_dend = FALSE,
  show_row_names = FALSE,
  show_column_names = FALSE,
  heatmap_legend_param = list(
    at = as.integer(names(delsieve.gt.legend)),
    labels = delsieve.gt.legend,
    title = "Genotype",
    grid_height = unit(3, "mm"),
    grid_width = unit(3, "mm"),
    color_bar = "discrete",
    border = "black",
    title_gp = gpar.title,
    labels_gp = gpar.text
  ),
  top_annotation = gt.key.sites,
  # bottom_annotation = cn.info.for.gt,
  use_raster = FALSE
)

draw(delsieve.gt.hm)

dev.off()
```

### Comparison of calling deletions between DelSIEVE and Sequenza

```{r}
cov.comp.anno.data <- get.cov.comp(
  cell.origin = list(
    "Cancer" = ".+"
  ),
  ref.cn.comp,
  delsieve.gt.data,
  cov.data,
  list(
    c("CN<2\nSequenza", "CN>=2\nSequenza"),
    c("CN<2\nSequenza", "Deletion\nDelSIEVE"),
    c("Deletion\nDelSIEVE", "Neutral\nDelSIEVE")
  )
)
```

```{r}
plots <- plot.cov.comp(
  cov.comp.anno.data$comp,
  "clone",
  cov.comp.anno.data$anno,
  "smd_estimate",
  group.name.map = list(
    "Cancer" = NULL
  ),
  anno.sep = 16,
  title.suffix = " in TNBC16"
)

lapply(
  names(plots),
  function(x) {
    ggsave(
      paste0(DELSIEVE_PREFIX, "/geneannotator/del_comp_3_", x, ".pdf"),
      plots[[x]] + theme(legend.position = "none"),
      device = "pdf",
      width = 178,
      height = 55,
      units = "mm"
    )
  }
)
```

```{r}
sieveVCF <- readRDS(SIEVE_VCF)
sieve.gt.data <- get.ternary(sieveVCF)

targeted.sites <- unique(c(
  rownames(delsieve.gt.data)[(rowSums(delsieve.gt.data < 0) > 0)],
  rownames(sieve.gt.data)[(rowSums(sieve.gt.data > 1) > 0)]
))

length(intersect(
  rownames(delsieve.gt.data)[(rowSums(delsieve.gt.data < 0) > 0)],
  rownames(sieve.gt.data)[(rowSums(sieve.gt.data > 1) > 0)]
))

all(rowSums(sieve.gt.data[
  setdiff(
    rownames(delsieve.gt.data)[(rowSums(delsieve.gt.data < 0) > 0)],
    rownames(sieve.gt.data)[(rowSums(sieve.gt.data > 1) > 0)]
  ), ] == 1) > 0)

targeted.delsieve.gt.data <- delsieve.gt.data[targeted.sites, ]
targeted.sieve.gt.data <- sieve.gt.data[targeted.sites, ]

length(rownames(delsieve.gt.data)[(rowSums(delsieve.gt.data < 0) > 0)])
length(rownames(delsieve.gt.data)[(rowSums(delsieve.gt.data > 1) > 0)])
length(rownames(sieve.gt.data)[(rowSums(sieve.gt.data > 1) > 0)])

setdiff(rownames(sieve.gt.data), rownames(delsieve.gt.data))
```

### ADO state heatmap from Sieve

Cells are ordered according to the above tree, and sites are ordered with a specified distance method.

```{r}
# sieve.ado.data <- get.ado.state(sieveVCF)
# ado.legend <- get.legend(sieve.ado.data, is.ado = TRUE)
#
# # sieve.ado.hm <- Heatmap(
# #   t(sieve.ado.data),
# #   col = color.gt.hm,
# #   row_title = hm.row.title,
# #   row_title_side = hm.row.title.side,
# #   row_title_gp = hm.row.title.gp,
# #   column_title = hm.column.title,
# #   column_title_side = hm.column.title.side,
# #   column_title_gp = hm.column.title.gp,
# #   cluster_rows = FALSE,
# #   row_order = hm.row.order,
# #   row_names_side = hm.row.names.side,
# #   row_names_gp = hm.row.names.gp,
# #   row_names_centered = TRUE,
# #   show_column_dend = FALSE,
# #   show_column_names = FALSE,
# #   heatmap_legend_param = list(
# #     at = as.integer(names(ado.legend)),
# #     labels = ado.legend,
# #     title = "ADO state",
# #     grid_height = unit(3, "mm"),
# #     grid_width = unit(3, "mm"),
# #     color_bar = "discrete",
# #     border = "black",
# #     title_gp = gpar.title,
# #     labels_gp = gpar.text
# #   ),
# #   use_raster = FALSE
# # )
# #
# # draw(sieve.ado.hm)
# #
# # sieve.ado.hm.column.order <- column_order(sieve.ado.hm)
# #
# # ado.key.sites <- columnAnnotation(
# #     labelled_sites = anno_mark(
# #       at = c(
# #         sieve.ado.hm.column.order[1L],
# #         sieve.ado.hm.column.order[2000L],
# #         sieve.ado.hm.column.order[4000L],
# #         sieve.ado.hm.column.order[length(sieve.ado.hm.column.order)]
# #         ),
# #       labels = get.formatted.num.as.char(c(
# #         "1",
# #         "2000",
# #         "4000",
# #         as.character(length(sieve.ado.hm.column.order))
# #         )),
# #       which = "column",
# #       side = "top",
# #       labels_gp = gpar.text,
# #       labels_rot = 0,
# #       link_width = unit(0.7, "mm"),
# #       link_height = unit(0.7, "mm")
# #     ),
# #     show_legend = FALSE
# #   )
# #
# # sieve.ado.hm.column.order <- rownames(sieveVCF)[sieve.ado.hm.column.order]
#
# cairo_pdf(
#   paste(SIEVE_PREFIX, "geneannotator/ado_sieve.pdf", sep = "/"),
#   width = out.gt.hm.width / in2mm,
#   height = out.gt.hm.height / in2mm,
#   onefile = FALSE
# )
#
# sieve.ado.hm <- Heatmap(
#   t(sieve.ado.data),
#   col = color.gt.hm,
#   row_title = hm.row.title,
#   row_title_side = hm.row.title.side,
#   row_title_gp = hm.row.title.gp,
#   column_title = hm.column.title,
#   column_title_side = hm.column.title.side,
#   column_title_gp = hm.column.title.gp,
#   cluster_rows = FALSE,
#   row_order = hm.row.order,
#   column_order = sieve.gt.hm.column.order,
#   row_names_side = hm.row.names.side,
#   row_names_gp = hm.row.names.gp,
#   row_names_centered = TRUE,
#   show_column_dend = FALSE,
#   show_column_names = FALSE,
#   heatmap_legend_param = list(
#     at = as.integer(names(ado.legend)),
#     labels = ado.legend,
#     title = "ADO state",
#     grid_height = unit(3, "mm"),
#     grid_width = unit(3, "mm"),
#     color_bar = "discrete",
#     border = "black",
#     title_gp = gpar.title,
#     labels_gp = gpar.text
#   ),
#   top_annotation = gt.key.sites,
#   use_raster = FALSE
# )
#
# draw(sieve.ado.hm)
#
# dev.off()
```

```{r}
library(xtable)
delsieve.gt.stats <- get.genotype.stats(delsieveVCF)
sieve.gt.stats <- get.genotype.stats(sieveVCF)
saveRDS(
  matrix(
    (c(delsieve.gt.stats, sieve.gt.stats)),
    nrow = 2,
    byrow = TRUE,
    dimnames = list(
      c("DelSIEVE", "SIEVE"),
      names(delsieve.gt.stats)
    )
  ),
  paste(DELSIEVE_PREFIX, "geneannotator/gt_prop.rds", sep = "/")
)
readRDS(paste(DELSIEVE_PREFIX, "geneannotator/gt_prop.rds", sep = "/"))
print(xtable(format(readRDS(paste(DELSIEVE_PREFIX, "geneannotator/gt_prop.rds", sep = "/")), digits = 3L, scientific = TRUE), type = "latex"))
```

```{r}
ggplot(
  tibble(
    label = names(delsieve.gt.stats),
    prop = delsieve.gt.stats * 100
  ) %>%
    mutate(
      ypos = cumsum(prop) - 1 * prop
    ),
  aes(
    x = "",
    y = prop,
    fill = label
  )
) +
  geom_bar(
    stat = "identity",
    width = 1,
    color = "white"
  ) +
  coord_polar(
    "y",
    start = 0
  ) +
  theme_void() +
  theme(legend.position="none") +
  geom_text(
    aes(
      y = ypos,
      label = label
    ),
    color = "white",
    size = 6
  ) +
  scale_fill_brewer(palette = "Set1")
```
